\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{black}

\nopagenumbers{}

\usepackage{lmodern}

\name{Kristaps}{Bebris}
\title{Software Developer}

\input{contacts.tex}
\phone[mobile]{\contactmobile}
\email{\contactemail}

\social[linkedin]{kristaps-bebris-76521061}
\social[github]{kristapsbe}

\begin{document}
\makecvtitle

\section{Summary}
\cvitem{}{I'm an enthusiastic professional with more than 10 years of software development experience. I love learning new things and solving interesting problems. I have a Masters degree in Bioinformatics, and a passion for machine learning, artificial intelligence, and everything related.}

%\cventry {<year --year >}{< degree/job title >}{< institution /employer >}
%{<city >}{< grade >}{< description >}
\section{Experience}
\cventry{2024 -- Now}{Software Engineer}{GoCardless}{Riga, Latvia}
{}{Working on improving and expanding based open banking services. \newline Primarily working with Python, Django, Kubernetes, and Terraform. Occasionally working with Ruby, and Typescript.}
\cventry{2019 -- 2024}{Data Scientist}{Sannsyn}{Riga, Latvia}
{}{I worked on data analysis projects, semantic search, and consulted clients. \newline Primarily worked with Python, Databricks, C\#, Kotlin, and Typescript.}
\cventry{2020 -- 2020}{Research Assistant}{University of Latvia}{Riga, Latvia}
{}{I developed a pipeline for metagenomic analysis. \newline Primarily worked with StaG-mwc.}
\cventry{2017 -- 2019}{Data Scientist}{Emergn}{Riga, Latvia}
{}{I lead the development of machine learning based prototypes, tools, and services. \newline Primarily worked with Python, assorted ML libraries, and Flask.}
\cventry{2012 -- 2017}{Software Developer}{Emergn}{Riga, Latvia}
{}{I developed and maintained an enterprise application distribution system, and developed and maintained travel websites. \newline Primarily worked with PHP, Javascript, and Java.}

\section{Education}
\cventry{2015 -- 2017}{MSc}{Uppsala University}{Uppsala, Sweden}
{}{Bioinformatics. \newline “Local adaptation of Grauer’s gorilla gut microbiome”}
\cventry{2010 -- 2013}{BEng}{Riga Technical University}{Riga, Latvia}
{}{Information Technology. \newline “Usage of genetic algorithms in the construction of decision trees”}

\end{document}
